---
title: "Starting small: The origins of successor function knowledge in subset knowers"
bibliography: citations.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    <!-- \author{{\large \bf Rose M. Schneider},^1  {\large \bf Ashlie H. Pankonin},^2 {\large \bf Adena Schachner},^1, $\&$ {\large \bf David Barner}^1 -->
    <!-- \\ ^1Department of Psychology, University of California, San Diego \\ -->
    <!-- ^2 School of Speech, Language, and Hearing Sciences, San Diego State University} -->

abstract: >
    Include no author information in the initial submission, to facilitate
    blind review.  The abstract should be one paragraph, indented 1/8 inch on both sides,
    in 9~point font with single spacing. The heading 'Abstract'
    should be 10~point, bold, centered, with one line of space below
    it. This one-paragraph abstract section is required only for standard
    six page proceedings papers. Following the abstract should be a blank
    line, followed by the header 'Keywords' and a list of
    descriptive keywords separated by semicolons, all in 9~point font, as
    shown below.
    
keywords: >
    Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term.
    
output: cogsci2016::cogsci_paper
# final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, include = FALSE}
rm(list = ls())
require("knitr")
# opts_knit$set(root.dir = "~/Documents/Projects/small_sf/") #this is specific to RMS, change accordingly
library(tidyverse)
library(magrittr)
library(langcog)
library(lme4)
library(stringr)
library(RColorBrewer)
library(ggthemes)
library(memisc)
'%!in%' <- function(x,y)!('%in%'(x,y))
```

```{r}
####DATA LOADING AND MANAGEMENT
#load study 1 data
data.raw.study1 <- read.csv("../../Data/small_sf_study1.csv")
data.raw.study2 <- read.csv("../../Data/small_sf_study2.csv")

##Exclude any pilots and copypaste
data.raw.study1 %<>%
  filter(SID != "CopyPasteMe", 
         Exclusion_reason != "Pilot")%>%
  droplevels()%>%
  # dplyr::select(-X, -X.1, -X.2, -X.3, -X.4)%>%
  mutate(Age = as.numeric(as.character(Age)))

data.raw.study2 %<>%
  filter(SID != "CopyPasteMe", 
         Exclusion_reason != "Pilot")%>%
  droplevels()%>%
  # dplyr::select(-X, -X.1, -X.2, -X.3, -X.4)%>%
  mutate(Age = as.numeric(as.character(Age)))

#how many kids pre-exclusions?
#exp.1
pre.excl.exp.1 <- data.raw.study1 %>%
  distinct(SID, Age)%>%
  summarise(n = n())

#exp.2
pre.excl.exp2 <- data.raw.study2 %>%
  distinct(SID, Age)%>%
  summarise(n = n())

#Why are kids excluded?
#exp.1
excl.reason.exp1 <- data.raw.study1 %>%
  filter(Exclude == 1)%>%
  distinct(SID, Exclude, Exclusion_reason)%>%
  group_by(Exclusion_reason)%>%
  summarise(n = n())
#exp.2
excl.reason.exp2 <- data.raw.study2 %>%
  filter(Exclude == 1)%>%
  distinct(SID, Exclude, Exclusion_reason)%>%
  group_by(Exclusion_reason)%>%
  summarise(n = n())

#### GLOBAL EXCLUSIONS
#exp.1
data.raw.study1 %<>%
  filter(Exclude != 1)%>%
  droplevels()
#exp.2
data.raw.study2 %<>%
  filter(Exclude != 1)%>%
  droplevels()

#### TRIAL/TASK EXCLUSIONS
#exp.1
data.raw.study1 %<>%
  mutate(Exclude_trial = ifelse(is.na(Exclude_trial), "0", as.character(Exclude_trial)))%>%
  filter(Exclude_trial != "1")

#exp.2
data.raw.study2 %<>%
  mutate(Exclude_trial = ifelse(is.na(Exclude_trial), "0", as.character(Exclude_trial)))%>%
  filter(Exclude_trial != "1")


#how many kids failed training for SF?
#exp.1
fail.sf.training.exp1 <- data.raw.study1 %>%
  filter(Task == "SF", 
         Trial_number == "Training", 
         Correct == "0")%>%
  summarise(n = n())

#exp.2
fail.sf.training.exp2 <- data.raw.study2 %>%
  filter(Task == "SF", 
         Trial_number == "Training", 
         Correct == "0")%>%
  summarise(n = n())

##exclude training for SF
#exp.1
data.raw.study1 %<>%
  mutate(Trial_number = ifelse(is.na(Trial_number), "HC", as.character(Trial_number)))%>%
  filter(Trial_number != "Training")

##exclude training for SF
#exp.2
data.raw.study2 %<>%
  mutate(Trial_number = ifelse(is.na(Trial_number), "HC", as.character(Trial_number)))%>%
  filter(Trial_number != "Training")

#Exclude training for NN
data.raw.study2 %<>%
  mutate(Trial_number = ifelse(is.na(Trial_number), "HC", as.character(Trial_number)), 
         Exclude_NN = ifelse((Task == "Next_number" & Trial_number == "1"), 1, 0))%>%
  filter(Exclude_NN != 1)

## RENAME ABOVE FOR SIMPLICITY
all.data.study1 <- data.raw.study1

all.data.study2 <- data.raw.study2
```

```{r, include = FALSE}
# Data validation
## Checking knower level classifications
#study 1
given.ms <- all.data.study1 %>%
  mutate(Knower_level = ifelse(Knower_level == "CP", 6, as.numeric(as.character(Knower_level)))) %>% #for function below
  filter(Task == "Give_N", 
         !is.na(Task_item))%>%
  group_by(SID, Knower_level, Task_item)%>%
  summarise(mean = mean(as.numeric(as.character(Correct)), na.rm = TRUE))

#overall check - an N-knower should have gotten at least .67 mean performance for a given N
check <- given.ms %>%
  filter(Task_item == Knower_level)%>%
  filter(mean < .66)

if(length(check$SID) > 0) {
  print("CHECK STUDY 1 KLs")
}

#study 2
given.ms <- all.data.study2 %>%
  mutate(Knower_level = ifelse(Knower_level == "CP", 6, as.numeric(as.character(Knower_level)))) %>% #for function below
  filter(Task == "Give_N", 
         !is.na(Task_item))%>%
  group_by(SID, Knower_level, Task_item)%>%
  summarise(mean = mean(as.numeric(as.character(Correct)), na.rm = TRUE))

#overall check - an N-knower should have gotten at least .67 mean performance for a given N
check <- given.ms %>%
  filter(Task_item == Knower_level)%>%
  filter(mean < .66)

if(length(check$SID) > 0) {
  print("CHECK STUDY 2 KLs")
}
```

```{r}
#change correct to numeric
all.data.study1 %<>%
  mutate(Correct = as.numeric(as.character(Correct)))

all.data.study2 %<>%
  mutate(Correct = as.numeric(as.character(Correct)))
```

```{r}
##add CP_subset
#by CP_subset
#Study 1 
all.data.study1 %<>%
  mutate(CP_subset = ifelse(Knower_level == "CP", "CP", 
                            "Subset"))
#Study 2 
all.data.study2 %<>%
  mutate(CP_subset = ifelse(Knower_level == "CP", "CP", 
                            "Subset"))
```

# Introduction

Introduction goes here!

# Experiment 1

## Method

### Participants

```{r exp1.demos}
exp.1.demos.age <- all.data.study1 %>%
  distinct(SID, CP_subset, Age)%>%
  group_by(CP_subset)%>%
  summarise(n = n(), 
            mean_age = round(mean(Age, na.rm = TRUE), 2), 
            sd_age = round(sd(Age, na.rm = TRUE), 2))%>%
  mutate(total.n = sum(n))

exp1.demos.sex <- all.data.study1 %>%
  distinct(SID, Sex)%>%
  group_by(Sex)%>%
  summarise(n = n())%>%
  mutate(total.n = sum(n))


### by n-knower level
n.levels.exp1 <- all.data.study1 %>%
  group_by(Knower_level)%>%
  distinct(SID, Age, Knower_level)%>%
  summarise(n = n(),
            mean_age = round(mean(Age, na.rm = TRUE), 2),
            sd_age = round(sd(Age, na.rm = TRUE),2))

```

We recruited `r exp.1.demos.age$total.n[1]` participants between the ages of 2 and 4 years (`r subset(exp1.demos.sex, Sex == "F")$total.n` female, $M_{age} =$ `r round(mean(all.data.study1$Age, na.rm = TRUE), 2)`, $SD_{age} =$ `r round(sd(all.data.study1$Age, na.rm = TRUE),2)`, range $=$ `r round(min(all.data.study1$Age),2)`-`r round(max(all.data.study1$Age),2)` years) from local preschools and the surrounding community in San Diego, US. `r subset(exp.1.demos.age, CP_subset == "Subset")$n` of these children were classified as subset knowers and `r subset(exp.1.demos.age, CP_subset == "CP")$n` were classified as CP-knowers using the Give-N task. The breakdown of \emph{N}-knower level classifications is shown in \ref{tab:demos1}.

\begin{table}[h]
\centering
\begin{tabular}{c c c } 
 \hline
 \emph{N}-knower level & \emph{n} & $M_{age}$ (SD) \\
 \hline
 1-knower & `r n.levels.exp1$n[1]` & `r n.levels.exp1$mean_age[1]` (`r n.levels.exp1$sd_age[1]`)\\
 2-knower & `r n.levels.exp1$n[2]` & `r n.levels.exp1$mean_age[2]` (`r n.levels.exp1$sd_age[2]`)\\ 
 3-knower & `r n.levels.exp1$n[3]` & `r n.levels.exp1$mean_age[3]` (`r n.levels.exp1$sd_age[3]`)\\
 4-knower & `r n.levels.exp1$n[4]` & `r n.levels.exp1$mean_age[4]` (`r n.levels.exp1$sd_age[4]`)\\
 CP-knower & `r n.levels.exp1$n[5]` & `r n.levels.exp1$mean_age[5]` (`r n.levels.exp1$sd_age[5]`)\\
 \hline
\end{tabular}
\caption{Demographics for all participants by knower level classification.}
\label{tab:demos1}
\end{table} 

### Stimuli

### Procedure

## Results and Discussion

# Experiment 2

## Method

### Participants
```{r exp2.demos}
exp.2.demos.age <- all.data.study2 %>%
  distinct(SID, CP_subset, Age)%>%
  group_by(CP_subset)%>%
  summarise(n = n(), 
            mean_age = round(mean(Age, na.rm = TRUE), 2), 
            sd_age = round(sd(Age, na.rm = TRUE), 2))%>%
  mutate(total.n = sum(n))

exp2.demos.sex <- all.data.study2 %>%
  distinct(SID, Sex)%>%
  group_by(Sex)%>%
  summarise(n = n())%>%
  mutate(total.n = sum(n))


### by n-knower level
n.levels.exp2 <- all.data.study2 %>%
  group_by(Knower_level)%>%
  distinct(SID, Age, Knower_level)%>%
  summarise(n = n(),
            mean_age = round(mean(Age, na.rm = TRUE), 2),
            sd_age = round(sd(Age, na.rm = TRUE),2))

```

We recruited `r exp.2.demos.age$total.n[1]` participants between the ages of 2 and 4 years (`r subset(exp2.demos.sex, Sex == "F")$total.n` female, $M_{age} =$ `r round(mean(all.data.study2$Age, na.rm = TRUE), 2)`, $SD_{age} =$ `r round(sd(all.data.study2$Age, na.rm = TRUE),2)`, range $=$ `r round(min(all.data.study2$Age),2)`-`r round(max(all.data.study2$Age),2)` years) from local preschools and the surrounding community in San Diego, US. `r subset(exp.2.demos.age, CP_subset == "Subset")$n` of these children were classified as subset knowers and `r subset(exp.2.demos.age, CP_subset == "CP")$n` were classified as CP-knowers using the Give-N task. The breakdown of \emph{N}-knower level classifications is shown in \ref{tab:demos2}.

\begin{table}[h]
\centering
\begin{tabular}{c c c } 
 \hline
 \emph{N}-knower level & \emph{n} & $M_{age}$ (SD) \\
 \hline
 1-knower & `r n.levels.exp2$n[1]` & `r n.levels.exp2$mean_age[1]` (`r n.levels.exp2$sd_age[1]`)\\
 2-knower & `r n.levels.exp2$n[2]` & `r n.levels.exp2$mean_age[2]` (`r n.levels.exp2$sd_age[2]`)\\ 
 3-knower & `r n.levels.exp2$n[3]` & `r n.levels.exp2$mean_age[3]` (`r n.levels.exp2$sd_age[3]`)\\
 4-knower & `r n.levels.exp2$n[4]` & `r n.levels.exp2$mean_age[4]` (`r n.levels.exp2$sd_age[4]`)\\
 5-knower & `r n.levels.exp2$n[5]` & `r n.levels.exp2$mean_age[5]`\\
 CP-knower & `r n.levels.exp2$n[6]` & `r n.levels.exp2$mean_age[6]` (`r n.levels.exp2$sd_age[6]`)\\
 \hline
\end{tabular}
\caption{Demographics for all participants by knower level classification.}
\label{tab:demos2}
\end{table} 

### Stimuli

### Procedure

## Results and Discussion

# General Discussion

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
